Reproducible Validation and Replication Studies in Nanoscale Physics

### 2020-07-26 tex/discussion.tex
ad discussion on ellis res

The second replication cases come from a paper by Ellis and co-workers \cite{ellis2016} studying the effect of aspect ratio on the excitation of high-order modes in localized surface phonon-polariton nanostructures. 
Their results in Figure 2 include experiments and simulations with the commercial software COMSOL, so we sought to both validate \pygbe using their experimental results, and replicate their computational findings. 
Again, we lack access to the data behind the plots, and we had to digitize the curves by hand. 
The quantity plotted in the original figures is reflectance as a function of wavenumber, whereas we compute the extinction---on the figures, they show inverted peaks, where we show positive peaks.
We can compare the results, nevertheless, because the quantity of interest is the wavenumber position of the peaks.
Figure \ref{fig:pygbe_vs_exp_2a} shows the results of our simulations using \pygbe on an isolated pillar,
compared with the experimental results of Ellis et al.\ on an array of pillars.
The results with \pygbe  do not account for the effect of coupling among the pillars, which explains the noticeable discrepancy on the wave numbers at which the peaks occur. 
We proposed a correction, based on the results reported on Figure S4 of Ellis et al.\ for the $AR=4$ case, where the shift on the wave number due to coupling is 12.17 cm$^{-1}$ (this value was obtained from digitized data). 
We subtract this value to that obtained with our simulations and we show the comparison of our corrected results against those of Ellis et al.: the experimental data on Figure \ref{fig:val_2a}, and the
computational data on Figure \ref{fig:rep_2a}. 
With this correction, we observe a good match of the wavenumber for the lower (and stronger) mode, while for the remaining modes a difference remains.

>>>>

The second replication case come from a paper by Ellis and co-workers \cite{ellis2016} studying the effect of aspect ratio on the excitation of high-order modes in localized surface phonon-polariton nanostructures (Figure S4 of their supplementary material).
Figure \ref{fig:rep_FS4_ellis} shows the results for this replication, where the relative errors between our computations and theirs is always smaller than 2$\%$. Having the smallest error for the case of $AR=4$ we proceed to study the results on Figure 2 of their work, which corresponds to teh same aspect ratio.
Their results in Figure 2 include experiments and simulations with the commercial software COMSOL, so we sought to both validate \pygbe using their experimental results, and replicate their computational findings. 
Again, we lack access to the data behind the plots, and we had to digitize the curves by hand. 
The quantity plotted in the original figures is reflectance as a function of wavenumber, whereas we compute the extinction---on the figures, they show inverted peaks, where we show positive peaks.
We can compare the results, nevertheless, because the quantity of interest is the wavenumber position of the peaks.
Figure \ref{fig:pygbe_vs_exp_2a} shows the results of our simulations using \pygbe on an isolated pillar,
compared with the experimental results of Ellis et al.\ on an array of pillars.
The results with \pygbe  do not account for the effect of coupling among the pillars, which explains the noticeable discrepancy on the wave numbers at which the peaks occur. 
We proposed a correction, based on the results reported on Figure S4 of Ellis et al.\ for the $AR=4$ case, where the shift on the wave number due to coupling is 12.17 cm$^{-1}$ (difference between black and red curve for AR=4 on figure S4 of supplementary material). 
We subtract this value to that obtained with our simulations and we show the comparison of our corrected results against those of Ellis et al.: the experimental data on Figure \ref{fig:val_2a}, and the
computational data on Figure \ref{fig:rep_2a}. 
When comparing with their experiments, once applied the correction, we observe a good match of the wavenumber for the lower (and stronger) mode, as well as a good match for the 
third and fourth peaks. The wave number of the second peak, related to a longitudinal excitation (mode $L_{000}$ on Ellis et al.), presents a discrepancy that we believe it is related to the fact that our 
pillar does not have a substrate underneath. The remaining (fifth) peak, also presents a discrepancy, but in this case we can not identify the reason.
It is worth mentioning that we do not include in the analysis the far left and far right peaks seen in the experimental results, since Ellis et al. do not discuss their 
presence in detail (NOT SURE HOW TO FULLY EXPLAIN THIS.)
